### 2017-01-31 grlp.tex
changed intro

@@

\section{Generalized Reduced Linear Program}

@@

The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation. 
To understand this, we need to look at the Lagrangian of the ALP and GRLP in 
\eqref{lag} and \eqref{lag2} respectively, i.e., 
\begin{align}\label{lag}
\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
Thus, when $Wq = \lambda$, i.e., when $W$ is a set of basis functions that allow
a low dimensional linear representation of the dual variables $\lambda$,
the two problems are the same.
%Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers. 
Hence, while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$). 
%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. 
To get a sense of how $W$ should be chosen, recall that
the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e., 
\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$) \cite{dolgov}. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.
\subsection{Novel Projection Operators}

@@

%\input{cartoon}
\subsection{Error Bounds}
\begin{theorem}[Error Bound for GRLP]
\label{cmt2mn}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
It holds that
\begin{align*}%\label{finalbndmn}
\begin{split}
||J^*-\hj||_{1,c}
\leq\frac{1}{1-\alpha}(6 ||J^*-\Phi r^*||_{\infty}
+2||\Gamma J^*-\hg J^*||_{\infty}).
\end{split}
\end{align*}
\end{theorem}
\begin{comment}
\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
Then,
\begin{align}\label{polthebnd}
%||J_{\hu}-\hj||_{1,c}
\norm{J^* - J_{\hu}}_{1,c}
&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\infty}
\nn\\&
+||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big).
\end{align}
\end{theorem}
\end{comment}
\begin{theorem}[Constraint Sampling]\label{st}
Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
$W_{s'a,i}=\delta_{s=s'}$.
Then
\begin{align*}%\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align*}
\end{theorem}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
In particular, the error term $\parallel\Gamma J^*-\tg J^* \parallel$ gives new insights into constraint selection. 
The result of Theorem~\ref{st} is that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.
\begin{comment}
\subsection{Comparison with ADP methods}
A host of the ADP methods such as \cite{lspi,lspe,lstd,Tsit} are based on solving the projected Bellman equation (PBE). The PBE based methods have been empirically successful and also have theoretical guarantees for the approximate value function. However, a significant shortcoming is that they suffer from the issue of \emph{policy-chattering} (see section~$6.4.3$ of \cite{BertB}), i.e., the sequence of policies might oscillate within a set of bad policies. A salient feature of the ALP based methods is that they find only one approximate value function $\tj$ and one sub-optimal policy derived as a greedy policy with respect to $\tj$. As a result there is no such issue of policy-chattering for the ALP based methods. By providing the error bounds for the GRLP, our paper provides the much required theoretical support for the RLP. Our GRLP framework closes the long-standing gap in the literature of providing a theoretical framework to bound the error due to constraint reduction in ALP based schemes.\\

\FloatBarrier
\begin{table}[H]
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|}\hline
ADP Method	&Empirical	&Theoretical\\\hline
Projected Bellman &\ding{51}    &\ding{53}-Policy Chattering\\
Equation	&	&\\\hline
ALP		&\ding{53}-Large number of Constraints &\ding{51}\\\hline
RLP		&\ding{51} &\ding{53}-  Only under\\
&&ideal assumptions\\\hline
\end{tabular}
}
\end{table}
\end{comment}

>>>>

\begin{comment}

@@

\end{comment}
\section{Main Results}
\begin{comment}

@@

\end{comment}
%\subsection{Novel Projection Operators}

@@

%\input{cartoon}
\subsection{Error Bounds}
\begin{theorem}[Error Bound for GRLP]
\label{cmt2mn}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
It holds that
\begin{align*}%\label{finalbndmn}
\begin{split}
||J^*-\hj||_{1,c}
\leq\frac{1}{1-\alpha}(6 ||J^*-\Phi r^*||_{\infty}
+2||\Gamma J^*-\hg J^*||_{\infty}).
\end{split}
\end{align*}
\end{theorem}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
\begin{comment}
\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
Then,
\begin{align}\label{polthebnd}
%||J_{\hu}-\hj||_{1,c}
\norm{J^* - J_{\hu}}_{1,c}
&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\infty}
\nn\\&
+||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big).
\end{align}
\end{theorem}
\end{comment}
\begin{theorem}[Constraint Sampling]\label{st}
Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
$W_{s'a,i}=\delta_{s=s'}$.
Then
\begin{align*}%\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align*}
\end{theorem}
\begin{comment}
An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
In particular, the error term $\etmn$ gives new insights into constraint selection:
The result of Theorem~\ref{st} is that
\end{comment}
The additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
%The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.

### 2017-01-31 intro.tex
submitted_version
revised
changed intro

%!TEX root =  autocontgrlp.tex
\section{Introduction}
Markov decision processes (MDPs) are a powerful mathematical framework to study optimal sequential decision making problems  arising in science and engineering. The so-called dynamic programming methods find an optimal policy by computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states. MDPs with small number of states can be solved easily by conventional dynamic programming techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB}.

In this paper we consider the problem of using dynamic programming with MDPs with large state spaces.
A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$. %Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm. 
Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation. Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.

The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation. A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable. A way out is to choose a subset of constraints at random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP). The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}. An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was also found useful in experiments. However, to this date, there exist no theoretical guarantees bounding the loss in performance resulting from such an approximation.

In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
The salient aspects of our contribution are listed below:
\begin{enumerate}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}). 
		\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).
		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
		\item Our results on the GRLP are the first to theoretically analyze the use of linear function approximation of Langrangian (dual) variables underlying the constraints.
		\item A numerical example in controlled queues is provided to illustrate the theory.
\end{enumerate}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Introduction}
Markov decision processes (MDPs) are a powerful mathematical framework to study optimal sequential decision making problems  arising in science and engineering. In an MDP, the configuration of the system is described by the state variables (or simply the state) and the system evolves in a stochastic manner which depends on the action made. The set of all states is denoted by $S$, the state space and the set of all actions is denoted by $A$, the action space.
%An instance of an MDP is a controlled queue setting, where there is a cost associated with the number of customers in the queue, and the aim is to control the service level depending on the number of %customers so as to achieve a minimum cumulative cost. In more general terms, given any MDP,
We are interested in computing what is known as the optimal policy $u^*$ (a map from $S$ to $A$). The so-called dynamic programming (DP) methods first compute what is known as the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states, and use it to compute $u^*$. When the number of state is small conventional DP techniques, such as value-, or policy-iteration, or linear programming (LP) can be used to compute $J^*$ and $u^*$\cite{BertB}.\par
As the number of states is grows, it becomes increasingly difficult to compute the exact values of $J^*$ and $u^*$. A practical solution then is to compute an approximate value function $\tilde{J}$ instead of $J^*$. Approximate dynamic programming (ADP) methods combine an approximation architecture to represent $\tj$ and a conventional DP method to compute $\tj$. Eventually, ADP methods output a sub-optimal policy $\tu$ using the $\tj$ they compute. %Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm.\par
Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation. Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.\par
It is natural to expect that approximations lead to errors and it is important to quantify the errors. For a given ADP method, theoretical performance analysis analytically bounding the error terms $||J^*-\tilde{J}||$  and $\norm{J^*-J_{\tu}}$ which denote the error in approximating the value function, and performance loss due to following policy $\tu$ (here $J_{\tu}$ is the value of $\tu$) respectively. Further, in most cases the error terms reveal some structure that can offer insights and act as guide to the designer of the ADP method (for example the choice of $\Phi$). \par

%While many ADP methods use LFA, not all of them are successful. For instance, ADP methods that use linear least squares projection are known to exhibit `policy oscillations' \cite{dpchapter}, i.e., %output a repeating sequence of bad sub-optimal policies.
%Such an analysis is important to establish that the error is always bounded.
%Further, in most cases the error terms reveal some structure that can offer insights and act as guide to the designer of the ADP method (for example the choice of $\Phi$). \par

The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants combine LFA and the LP approach. Theoretical performance analysis of the ALP can be found in \cite{ALP}.
%and a salient feature is that it does not suffer from issues such as `policy oscillations'\footnote{ADP methods that use linear least squares projection are known to exhibit `policy oscillations' %\cite{BertB}, i.e., output a repeating sequence of bad sub-optimal policies. Since our focus in this paper is the ALP formulation, we refrain from a detailed presentation of the other methods.}

A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable. Two approaches have been found empircally successful in addressing the issue of large number of constraints in the ALP. In the first approach, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear program} (RLP). The performance analysis of the RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions. The second approach involves employing function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}. However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach.\par
Our motivation stems from the fact that ALP with tractable number of constraints will result in a full dimeniosnality free ADP method. However, constraint reduction in the ALP is an extra source of error (in addition to the error due to LFA), which has not been theoretically well understood.  The focus of this paper is to fill this gap in theory by deriving performance bounds for constraint reduction in the ALP formulation.
The salient aspects of our contribution are listed below:
\begin{enumerate}
\item We define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints. The GRLP amounts to linear function approximation of the dual variables, and the RLP is a special case of GRLP.
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}). 
		\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).
		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
%Our analysis also makes use of arguments based on \emph{Lyanpunov} function, an approach much similar to prior works in ALP literature \cite{ALP,SALP}.
\item Our results on the GRLP are the first to theoretically analyze the use of linear function approximation of Langrangian (dual) variables underlying the constraints.
\item A numerical example in controlled queues is provided to illustrate the theory.
\end{enumerate}
%ALP with tractable number of constraints would result in  a full dimensionality free ADP method, without issues such as policy oscillations.
A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.

### 2017-01-31 rel.tex
changed intro

%!TEX root =  autocontgrlp.tex
\begin{comment}
\section{Approximate Linear Programming: Successes and Challanges}
When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}. A practical solution is to resort to function approximation. Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$.
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\,\,\,
\text{s.t.}\mb \Phi r\geq T \Phi r,
\end{split}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $\Phi$ is a feature matrix whose first column is $\one$. Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy w.r.t. $\tj$.
The following is a preliminary error bound for the ALP from \cite{ALP}:
\begin{theorem}[Error Bound for ALP]
||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty
%For a more detailed treatment of the ALP and sophisticated bounds, the reader is referred to \cite{ALP}.
%\subsection{Approximating the Constraints}
The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables. Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques. Most works in literature make use of the underlying structure of the problem to cleverly reduce the number of constraints of the ALP. A good example is \cite{gkp}, wherein the structure in factored linear functions is exploited. The use of basis function also helps constraint reduction in \cite{Mor-Kum}. In \cite{ALP-Bor}, the constraints are approximated indirectly by approximating the square of the Lagrange multipliers. In \cite{petrik} the transitional error is reduced ignoring the representational and sampling errors.\par

@@

\end{comment}
\section{Main Results}
\begin{comment}
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
&\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
&\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}

@@

where we assume that $W \in \R^{nd\times m}_+$ is a matrix with all positive entries, $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution and $\tr \in \N$.
\footnote{The appendix explains how $\N$ can be chosen.}
In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.\par
\end{comment}
%\subsection{Novel Projection Operators}
We now define two projection operators which are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
%The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
\begin{definition}\label{lubpop}
Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to

@@

\label{lubplp}
\begin{split}
\underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,\mb
\text{s.t.} \mb \Phi r\geq  TJ.
\end{split}

@@

Then, for $J\in \R^n$, $\Gamma J$,
the \emph{ least upper bound projection} of $J$ is defined as
\begin{align}\label{gamdef}
(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
\end{definition}

%The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
The definition of the second operator is as follows:
\begin{definition}\label{alubpop}
Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}$ to be the solution to
\begin{align}\label{alubplp}
\underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,\mb
\text{s.t.} \,\,\, W^\top E \Phi r\geq W^\top HJ.
\end{align}
Then, the \emph{approximate least upper bound (ALUB) projection operator}
$\hg \colon \R^n \ra \R^n$ is defined as
\begin{align}\label{tgamdef}
(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,, J\in \R^n\,.
\end{align}
\end{definition}
\begin{remark}\label{ubrem}
To understand the meaning of $\Gamma$ (and $\hg$) define
\begin{align}\label{ubclass}
\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
\end{align}
where $J\in \R^n$.
Disregarding the constraint $r\in \N$,
$\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
\end{remark}

%\input{cartoon}
\subsection{Error Bounds}
\begin{theorem}[Error Bound for GRLP]
\label{cmt2mn}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
It holds that
\begin{align*}%\label{finalbndmn}
\begin{split}
||J^*-\hj||_{1,c}
\leq\frac{1}{1-\alpha}(6 ||J^*-\Phi r^*||_{\infty}
+2||\Gamma J^*-\hg J^*||_{\infty}).
\end{split}
\end{align*}
\end{theorem}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
\begin{comment}
\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
Then,
\begin{align}\label{polthebnd}
%||J_{\hu}-\hj||_{1,c}
\norm{J^* - J_{\hu}}_{1,c}
&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\infty}
\nn\\&
+||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big).
\end{align}
\end{theorem}
\end{comment}
\begin{theorem}[Constraint Sampling]\label{st}
Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
$W_{s'a,i}=\delta_{s=s'}$.
Then
\begin{align*}%\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align*}
\end{theorem}
\begin{comment}
An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
In particular, the error term $\etmn$ gives new insights into constraint selection:
The result of Theorem~\ref{st} is that
\end{comment}
The additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
%The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.

>>>>

\section{Related Work}
The following is a preliminary error bound for the ALP from \cite{ALP}:
\begin{theorem}[Error Bound for ALP]
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty
\end{align*}
\end{theorem}
%For a more detailed treatment of the ALP and sophisticated bounds, the reader is referred to \cite{ALP}.
%\subsection{Approximating the Constraints}
The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

Most works in literature make use of the underlying structure of the problem to cleverly reduce the number of constraints of the ALP. A good example is \cite{gkp}, wherein the structure in factored linear functions is exploited. The use of basis function also helps constraint reduction in \cite{Mor-Kum}. In \cite{ALP-Bor}, the constraints are approximated indirectly by approximating the square of the Lagrange multipliers. In \cite{petrik} the transitional error is reduced ignoring the representational and sampling errors.\par

@@

\subsection{Primal-Dual Approximation}
The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation.
To understand this, we need to look at the Lagrangian of the ALP and GRLP in
\eqref{lag} and \eqref{lag2} respectively, i.e.,
\begin{align}\label{lag}
\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).

@@

Thus, when $Wq = \lambda$, i.e., when $W$ is a set of basis functions that allow
a low dimensional linear representation of the dual variables $\lambda$,
the two problems are the same.
%Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers.
Hence, while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
To get a sense of how $W$ should be chosen, recall that
the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e.,

@@

\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn

@@

where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$) \cite{dolgov}. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.

\begin{comment}
\subsection{Comparison with ADP methods}
A host of the ADP methods such as \cite{lspi,lspe,lstd,Tsit} are based on solving the projected Bellman equation (PBE). The PBE based methods have been empirically successful and also have theoretical guarantees for the approximate value function. However, a significant shortcoming is that they suffer from the issue of \emph{policy-chattering} (see section~$6.4.3$ of \cite{BertB}), i.e., the sequence of policies might oscillate within a set of bad policies. A salient feature of the ALP based methods is that they find only one approximate value function $\tj$ and one sub-optimal policy derived as a greedy policy with respect to $\tj$. As a result there is no such issue of policy-chattering for the ALP based methods. By providing the error bounds for the GRLP, our paper provides the much required theoretical support for the RLP. Our GRLP framework closes the long-standing gap in the literature of providing a theoretical framework to bound the error due to constraint reduction in ALP based schemes.\\

\FloatBarrier
\begin{table}[H]
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|}\hline
ADP Method	&Empirical	&Theoretical\\\hline
Projected Bellman &\ding{51}    &\ding{53}-Policy Chattering\\
Equation	&	&\\\hline
ALP		&\ding{53}-Large number of Constraints &\ding{51}\\\hline
RLP		&\ding{51} &\ding{53}-  Only under\\
&&ideal assumptions\\\hline
\end{tabular}
}
\end{table}
\end{comment}
